A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-09-23 bioc-workflow.Rmd
more on unsupervised ML

As described and demonstrated already above, PCA is a valuable and
powerful method for data visualisation and quality control. We do not
do any unsupervised clustering in the frame of the above spatial
proteomics workflow as although clustering can be useful for grouping
labelled data into categories e.g. see the `mrkHClust` function, we do
not find it adaquete for protein localisation prediction and spatial
proteomics data analysis in general.

>>>>

As described and demonstrated already above, PCA is a valuable and
powerful method for data visualisation and quality control. We do not
do any unsupervised clustering in the frame of the above spatial
proteomics workflow as although clustering can be useful for grouping
labelled data into categories e.g. see the `mrkHClust` function, we do
not find it adaquete for spatial proteomics data analysis. We find
supervised learning more suited to the task of protein localisation
prediction in which we use high-quality curated marker proteins to
build a classifier, instead of using an entirely unsupervised approach
to look for clusters and then look for enrichment of organelles and
complexes. In the latter we do not make good use of valuable prior
knowledge, and in our experience unsupervised clustering can be
extremely difficult due poor estimates of the number of clusters that
may appear in the data.
